A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-23 latex/main.tex
Final changes pre submission

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methodology, software, resources, visualization
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Invesigation, data curation, formal analysis, validation
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
resources, JK;
supervision, JK;
funding acquisition, JK.

>>>>

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methodology, software, resources, visualization
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Invesigation, data curation, formal analysis, validation
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, SHZ, YW, AI, KE, IG, BJ, DSP, CLM, SPO, JK;
resources, JK;
supervision, JK;
funding acquisition, JK.
